Loading and preprocessing the data

```{r}
activity <- read.csv("./activity.csv")
activity$date <- as.Date(activity$date)
head(activity)
summary(activity)
```

What is mean total number of steps taken per day?

Histogram
```{r}
library(ggplot2)
stepsPlot<-qplot(date, weight=activity$steps, data=activity, geom="histogram")
print(stepsPlot)
```

Mean and Median
```{r}
mean(tapply(activity$steps, activity$date, sum, na.rm = TRUE))
median(tapply(activity$steps, activity$date, sum, na.rm = TRUE))
```

What is the average daily activity pattern?

Average Number of Steps Plot 
```{r}
average_steps<-data.frame(cbind(activity$interval,tapply(activity$steps, activity$interval, mean, na.rm = TRUE)))
colnames(average_steps) <- c("interval","steps")
averageStepsPlot<-ggplot(data=average_steps,aes(x=interval,y=steps)) +
  geom_line()
print(averageStepsPlot)
```

Maximum Steps
```{r}
maxtime<-average_steps[which.max(average_steps$steps),"interval"]
strftime( as.POSIXct(Sys.Date()) + as.difftime(round(maxtime/100), units="hours")+ as.difftime(maxtime%%100, units="mins"), "%r",tz="UTC") 
```

Imputing missing values

Missing Values
```{r}
sum(is.na(activity$steps))
```

Fixing Missing Values
```{r}
fixed<-activity
fixed[is.na(fixed[, 1]), 1]<-average_steps[is.na(fixed[, 1]),2]
```

Histogram
```{r}
qplot(date, weight=fixed$steps, data=fixed, geom="histogram")
```

Mean and Median
```{r}
mean(tapply(fixed$steps, fixed$date, sum, na.rm = TRUE))
median(tapply(fixed$steps, fixed$date, sum, na.rm = TRUE))
```

Are there differences in activity patterns between weekdays and weekends?

Weekday and Weekend
```{r}
library(lattice)
fixed$day<-as.factor(ifelse(weekdays(fixed$date) %in% c("Saturday","Sunday"),"Weekend","Weekday"))
```

Average step for Weekday/Weekend Plot
```{r}
xyplot(steps ~ interval | day, aggregate(steps ~ interval + day, fixed, FUN = mean), layout = c(1, 2), type = "l", group=day)
```